### 2008-06-23 tags/spark-08-submit/conclusion.tex
SPARK 2008 workshop submission

In this paper, we introduced two novel planning domains arising from
problems in natural language generation: the sentence generation domain and
the GIVE navigation domain. We also reported on the results of a number of
experiments in which we applied off-the-shelf planners to these domains.
Our main results were mixed. While modern planners do a pretty good job of
controlling the complexity of search, they also suffer from practical
problems that limit their performance in unexpected places. In particular,
in both domains the grounding step performed by both planners dominates the
time it takes to perform the search itself. The NLG community's recent
interest in planning also presents a valuable opportunity for planning
researchers: provided some of the challenges we have highlighted can be
addressed, projects like GIVE (and other NLG-inspired problem domains)
offer a constructive platform for the planning community to showcase their
techniques to a wider audience---and to improve the quality of their tools
for real-world planning tasks.

>>>>

In this paper, we introduced two novel planning domains arising from
problems in natural language generation: the sentence generation domain and
the GIVE navigation domain. We also reported on the results of a number of
experiments in which we applied off-the-shelf planners to these domains.
Our main results were mixed. While modern planners do a pretty good job of
controlling the complexity of search, they also suffer from practical
problems that limit their performance in unexpected ways. In particular,
in both domains the grounding step performed by both planners dominates the
time it takes to perform the search itself. The NLG community's recent
interest in planning also presents a valuable opportunity for planning
researchers: provided some of the challenges we have highlighted can be
addressed, projects like GIVE (and other NLG-inspired problem domains)
offer a constructive platform for the planning community to showcase their
techniques to a wider audience---and to improve the quality of their tools
for real-world planning tasks.
